---
title: "Hoehl_Anton_AssignmentV"
author: "Submitted by Anton Höhl (Student ID: 5637078)"
date: "04/02/2021"
output: 
  html_document:
    toc: true
---

<style>
body {
text-align: justify}
</style>

```{r echo=FALSE, include=FALSE}

library(tidyr)
library(dplyr)
library(ggplot2)
library(knitr)
library(textreadr)
library(httr)
library(rlist)
library(jsonlite)
library(maps)
```

## 0. Structure 

I (Anton Höhl Student ID: 5637078) worked together with Lana Kern (Student ID: 5395819), Michael Lyubkin (Student ID: 4168485), Jingwen Xu (Student ID: 5631584) and Martin Scheerer (Student ID: 5631373). I hereby confirm that my submission is in line with the "Code of Conduct" outlined on the lecture slides. While solving the Assignment each task will be shortly explained after solving it and if feasable an excerpt of the resulting data set is printed. Furthermore smaller steps will be explained in the code snippets as smaller comments to clarifiy the solution approach.  


## 1. Setting up a new GitHub repository

### The repository on Github can be found under the following Link: 
https://github.com/Anton-Hoehl/DSPM-Assignment.git


## 2. Getting to know the API

```{r API}
# read the api key from the rtf file
API_key <- read_rtf("API_key.rtf")

```


## 3. Interacting with the API - the basics

```{r API requests}
# create the request string
req_string <- paste("https://app.ticketmaster.com/discovery/v2/events?apikey=",
                    API_key,
                    "&locale=*&countryCode=DE", sep = "")

# get the request
response <- GET(url = req_string)
```


```{r contents}

# extract the contents
json <- content(x = response, as = "text" )

# convert from json to R object
r_obj <- fromJSON(json)

# retrive the venues from the object
venues <- as.data.frame(bind_rows(r_obj$`_embedded`$events$`_embedded`$venues,
                    .id = "column_label"))

# create empty df for the needed variables
venues_data <- setNames(
                  data.frame(
                    matrix(ncol = 7, nrow = length(venues$name))), 
                    c("name", "url","postalCode", "longitude",
                      "latitude", "city", "address"))

# select columns from the venues set   
venues_data$name <- venues$name
venues_data$url <- venues$url
venues_data$postalCode <- venues$postalCode
venues_data$longitude <- as.double(venues$location$longitude)
venues_data$latitude <- as.double(venues$location$latitude)
venues_data$city <- venues$city$name
venues_data$address <- venues$address$line1

# display the results
kable(venues_data, format = "html")
```

## 4. Interacting with the API - advanced

```{r all_venues}
# for loop which iterates over all pages 
all_venues <- data.frame()

for (page in c(0:25)){

  # create new request string
  req_string <- paste("https://app.ticketmaster.com/discovery/v2/venues?apikey="
                      ,API_key,
                      "&locale=*&size=500&page=", 
                      page ,
                      "&countryCode=DE",
                      sep = "")

  # get the new request
  response <- GET(url = req_string)

  json <- content(x = response, as = "text" )
  
  # convert from json to R object
  r_obj <- fromJSON(json)
  
  venues <- r_obj$`_embedded`$venues
  
  # select relevant columns and clean the frame 
  
  # set up df for the page frome the GET order
  venues_data <- setNames(
                    data.frame(
                      matrix(ncol = 7, nrow = length(venues$name))), 
                      c("name", "url","postalCode", "longitude",
                        "latitude", "city", "address"))
      
  venues_data$name <- venues$name
  venues_data$url <- venues$url
  venues_data$postalCode <- venues$postalCode
  venues_data$longitude <- as.double(venues$location$longitude)
  venues_data$latitude <- as.double(venues$location$latitude)
  venues_data$city <- venues$city$name
  venues_data$address <- venues$address$line1
  
  # add the new requested rows
  all_venues <- rbind(all_venues, venues_data)
  
  Sys.sleep(4)
}

```


## 5. Visualizing the extracted data

```{r Coordinate preparation}

# checking NAs
test <- all_venues[c("longitude", "latitude")]
test <- test[rowSums(is.na(test)) > 0,]

summary(test$latitude)
summary(test$longitude)

# copy venue set
mod_venues <- all_venues

# cut off  locations unlikely in Germany
mod_venues$long <- ifelse(between(mod_venues$longitude, 5.866944, 15.043611), 
                          mod_venues$longitude, 
                          NA)

mod_venues$lat <- ifelse(between(mod_venues$latitude, 47.271679, 55.0846), 
                          mod_venues$latitude, 
                          NA)


```




```{r Map}

# plot the German map including the venue locations
ggplot( ) + 
  geom_polygon(
        aes(x = long, y = lat, group = group), 
        data = map_data("world", region = "Germany"),
        fill = "grey90",color = "black") +
  theme_void() + 
  coord_quickmap() +
  geom_point(data = mod_venues, aes(x = long, y = lat), size = 0.5) +
  labs(title = "Event locations across Germany", 
       caption = "Source: ticketmaster.com") + 
  theme(title = element_text(size=8, face='bold'),
        plot.caption = element_text(face = "italic"))

```

## 6. Event locations in other countries

```{r all_venues}
# for loop which iterates over all pages 
all_venues <- data.frame()

for (page in c(0:39)){

  # create new request string
  req_string <- paste("https://app.ticketmaster.com/discovery/v2/venues?apikey="
                      ,API_key,
                      "&locale=*&size=500&page=", 
                      page ,
                      "&countryCode=FR",
                      sep = "")

  # get the new request
  response <- GET(url = req_string)

  json <- content(x = response, as = "text" )
  
  # convert from json to R object
  r_obj <- fromJSON(json)
  
  venues <- r_obj$`_embedded`$venues
  
  # select relevant columns and clean the frame 
  
  # set up df for the page frome the GET order
  venues_data <- setNames(
                    data.frame(
                      matrix(ncol = 7, nrow = length(venues$name))), 
                      c("name", "url","postalCode", "longitude",
                        "latitude", "city", "address"))
      
  venues_data$name <- venues$name
  venues_data$url <- venues$url
  venues_data$postalCode <- venues$postalCode
  venues_data$longitude <- as.double(venues$location$longitude)
  venues_data$latitude <- as.double(venues$location$latitude)
  venues_data$city <- venues$city$name
  venues_data$address <- venues$address$line1
  
  # add the new requested rows
  all_venues <- rbind(all_venues, venues_data)
  
  Sys.sleep(4)
}


# checking NAs
test <- all_venues[c("longitude", "latitude")]
test <- test[rowSums(is.na(test)) > 0,]

summary(test$latitude)
summary(test$longitude)

# copy venue set
mod_venues <- all_venues

# cut off  locations unlikely in Germany
mod_venues$long <- ifelse(between(mod_venues$longitude, -4.783333, 8.216667), 
                          mod_venues$longitude, 
                          NA)

mod_venues$lat <- ifelse(between(mod_venues$latitude, 42.333333, 51.083333), 
                          mod_venues$latitude, 
                          NA)


# plot the German map including the venue locations
ggplot( ) + 
  geom_polygon(
        aes(x = long, y = lat, group = group), 
        data = map_data("world", region = "France"),
        fill = "grey90",color = "black") +
  theme_void() + 
  coord_quickmap() +
  geom_point(data = mod_venues, aes(x = long, y = lat), size = 0.5) +
  labs(title = "Event locations across France", 
       caption = "Source: ticketmaster.com") + 
  theme(title = element_text(size=8, face='bold'),
        plot.caption = element_text(face = "italic"))

```




